Cosmology Essay: A review of Dark Matter and Dark Energy

### 2017-05-06 cosmology/Essay/CosmoEssayHK.tex
cosmology

\begin{thebibliography}{1}
\bibitem[Abbott et al(2015)]{abbott}Abott, T., et al (Dark Energy Survey Collaboration), 2015, The Dark Energy Survey: more than dark energy - an overview, arXiv:1601.00329v3
\bibitem[Amendola et al(2016)]{amendola}Amendola, L., et al (Euclid Theory Working Group), 2016, Cosmology and Fundamental Physics with the Euclid Satellite, arXiv:1006.00180v1
\bibitem[Arun et al(2017)]{arun}Arun, K., Gudennavar, S., B., Sivaram, C., 2017, Dark Matter, Dark Energy, and Alternate Models: A Review, arXiv:1704.06155
\bibitem[Baldry(2016)]{baldry}Baldry, I., Cosmology lecture notes - MSc Astrophysics, 2016, Not in public domain
\bibitem[Bergstrom(2012)]{bergstrom}Bergstrom L., 2012,  Dark Matter Evidence, Particle Physics Candidates and Detection Methods, arXiv:1205.4882
\bibitem[Bertone et al(2004)]{bertone2}Bertone, G., Hooper, D., Silk, J., 2004, Particle Dark Matter: Evidence, Candidates and Constraints, arXiv:hep-ph/0404175v2
\bibitem[Bertone and Hooper(2016)]{bertone1}Bertone, G., Hooper, D., 2016, A History of Dark Matter, arXiv:1605.04909v2
\bibitem[Calmet and Kuntz(2017)]{calmet}Calmet, X., Kuntz, I., 2017, What is modified gravity and how to differentiate it from particle dark matter?, arXiv:1702.03832v2
\bibitem[Clowe et al(2006)]{clowe}Clowe, D., Bradac, M., Gonzalez, A., H., Markevitch, M., Randall, S., W., Jones, C., Zaritsky, D., 2006, A Direct Empirical Proof of the Existence of Dark Matter, arXiv:astro-ph/0608407v1
\bibitem[Cohen-Tannoudji(2015)]{cohen}Cohen-Tannoudji, G., 2015, The dark universe and quantum vacuum, arXiv:1507.00460
\bibitem[Fornengo(2017)]{forengo}Fornengo, N., 2017, Dark matter overview, arXiv:1701.00119v3
\bibitem[Freese(2017)]{freese}Freese, K., 2017, Status of dark matter in the universe, arXiv:1701.01840v1
\bibitem[Gaggero et al(2016)]{gaggero}Gaggero, D., Bertone, G., Calore, F., Connors, R., M., T., Lovell, M., Markoff, S., Storm E., 2016, Searching for Primodial Black Holes in the radio and X-ray sky, arXiv:1612.00457v1
\bibitem[He Zhang(2017)]{he}He, H., Zhang, Z., 2017, Direct Probe of Dark Energy through Gravitational Lensing Effect, arXiv:1701.03418v2
\bibitem[Hill et al(2008)]{hill}Hill,G., J., et al, 2008, The Hobby-Eberly Telescope Dark Energy Experiment (HETDEX): Description and Early Pilot Survey Results, arXiv:0806.0183v1
\bibitem[Li et al(2012)]{li}Li, M., Li., X.,Wang, S., Wang, Y., 2012, Dark Energy: a Brief Review, arXiv:1209.0922v1
\bibitem[Lisanti(2016)]{lisanti}Lisante M, 2016, Lectures on Dark Matter Physics, arXiv:1603.03797v2
\bibitem[Mortonson et al(2013)]{mortonson}Mortonson, M., J., Weinberg, D., H., White, M., 2013, Dark Energy: A Short Review, arXiv:1401.0046v1
\bibitem[Novosyadlyj et al(2013)]{novos}Novosyadlyj, B., Pelykh, V., Zhuk, A., 2013, Dark Energy: Observational Evidence and Theoretical Models, arXiv:1502.04177
\bibitem[Ruben(1979)]{ruben}Ruben, V., C., Rotation curves of high-luminosity spiral galaxies and the rotation curve of our Galaxy, 1979, The large-scale characteristics of the galaxy; Proceedings of the Symposium, College Park, Md., June 12-17, 1978
\bibitem[Sellwood and Kosowsky(2000)]{sellwood}Sellwood, J., A., Kosowsky, A., 2000, Does Dark Matter Exist?, arXiv:astro-ph/0009074v1
\bibitem[de Swart et al(2017)]{swart}de Swart, J., Bertone, G., van Dongen, J., 2017, How Dark Matter Came to Matter, arXiv:1703.00013v1
\bibitem[Weinberg(2008)]{weinberg1}Weinberg, S., 2008, Cosmology, Oxford, 1st Edition
\bibitem[Weinberg et al(2013)]{weinberg2}Weinberg, D., H., Mortonson, M., J., Eisenstein, D., J.,Hirata, C., Riess, A., G., Rozo, E., 2013, Observational Probes of Cosmic Acceleration, arXiv:1201.2434v2
\bibitem[Zheng et al(2014)]{zheng}Zheng, W., Li, S., Xia, J., Li, M., Lu, T., 2014, Constraints on Dark Energy new New Observations including Pan-STARRS, arXiv:1405.2724v2
\bibitem[ESA (2013)]{planck}Planck, ESA, Planck reveals an almost perfect universe, Retrieved 5-5-2017
\end{thebibliography}
\end{document}

>>>>

\begin{thebibliography}{1}
\bibitem[Abbott et al(2015)]{abbott}Abott, T., et al (Dark Energy Survey Collaboration), 2015, The Dark Energy Survey: more than dark energy - an overview, arXiv:1601.00329v3
\bibitem[Amendola et al(2016)]{amendola}Amendola, L., et al (Euclid Theory Working Group), 2016, Cosmology and Fundamental Physics with the Euclid Satellite, arXiv:1006.00180v1
\bibitem[Arun et al(2017)]{arun}Arun, K., Gudennavar, S., B., Sivaram, C., 2017, Dark Matter, Dark Energy, and Alternate Models: A Review, arXiv:1704.06155
\bibitem[Baldry(2016)]{baldry}Baldry, I., Cosmology lecture notes - MSc Astrophysics, 2016, Not in public domain
\bibitem[Bergstrom(2012)]{bergstrom}Bergstrom L., 2012,  Dark Matter Evidence, Particle Physics Candidates and Detection Methods, arXiv:1205.4882
\bibitem[Bertone et al(2004)]{bertone2}Bertone, G., Hooper, D., Silk, J., 2004, Particle Dark Matter: Evidence, Candidates and Constraints, arXiv:hep-ph/0404175v2
\bibitem[Bertone and Hooper(2016)]{bertone1}Bertone, G., Hooper, D., 2016, A History of Dark Matter, arXiv:1605.04909v2
\bibitem[Calmet and Kuntz(2017)]{calmet}Calmet, X., Kuntz, I., 2017, What is modified gravity and how to differentiate it from particle dark matter?, arXiv:1702.03832v2
\bibitem[Clowe et al(2006)]{clowe}Clowe, D., Bradac, M., Gonzalez, A., H., Markevitch, M., Randall, S., W., Jones, C., Zaritsky, D., 2006, A Direct Empirical Proof of the Existence of Dark Matter, arXiv:astro-ph/0608407v1
\bibitem[Cohen-Tannoudji(2015)]{cohen}Cohen-Tannoudji, G., 2015, The dark universe and quantum vacuum, arXiv:1507.00460
\bibitem[ESA (2013)]{planck}Planck, ESA, http://www.esa.int/Our_Activities/Space_Science/Planck/Planck_reveals_an_almost_perfect_Universe, Retrieved 5-5-2017
\bibitem[Fornengo(2017)]{forengo}Fornengo, N., 2017, Dark matter overview, arXiv:1701.00119v3
\bibitem[Freese(2017)]{freese}Freese, K., 2017, Status of dark matter in the universe, arXiv:1701.01840v1
\bibitem[Gaggero et al(2016)]{gaggero}Gaggero, D., Bertone, G., Calore, F., Connors, R., M., T., Lovell, M., Markoff, S., Storm E., 2016, Searching for Primodial Black Holes in the radio and X-ray sky, arXiv:1612.00457v1
\bibitem[He Zhang(2017)]{he}He, H., Zhang, Z., 2017, Direct Probe of Dark Energy through Gravitational Lensing Effect, arXiv:1701.03418v2
\bibitem[Hill et al(2008)]{hill}Hill,G., J., et al, 2008, The Hobby-Eberly Telescope Dark Energy Experiment (HETDEX): Description and Early Pilot Survey Results, arXiv:0806.0183v1
\bibitem[Li et al(2012)]{li}Li, M., Li., X.,Wang, S., Wang, Y., 2012, Dark Energy: a Brief Review, arXiv:1209.0922v1
\bibitem[Lisanti(2016)]{lisanti}Lisante M, 2016, Lectures on Dark Matter Physics, arXiv:1603.03797v2
\bibitem[Mortonson et al(2013)]{mortonson}Mortonson, M., J., Weinberg, D., H., White, M., 2013, Dark Energy: A Short Review, arXiv:1401.0046v1
\bibitem[Novosyadlyj et al(2013)]{novos}Novosyadlyj, B., Pelykh, V., Zhuk, A., 2013, Dark Energy: Observational Evidence and Theoretical Models, arXiv:1502.04177
\bibitem[Ruben(1979)]{ruben}Ruben, V., C., Rotation curves of high-luminosity spiral galaxies and the rotation curve of our Galaxy, 1979, The large-scale characteristics of the galaxy; Proceedings of the Symposium, College Park, Md., June 12-17, 1978
\bibitem[Sellwood and Kosowsky(2000)]{sellwood}Sellwood, J., A., Kosowsky, A., 2000, Does Dark Matter Exist?, arXiv:astro-ph/0009074v1
\bibitem[de Swart et al(2017)]{swart}de Swart, J., Bertone, G., van Dongen, J., 2017, How Dark Matter Came to Matter, arXiv:1703.00013v1
\bibitem[Weinberg(2008)]{weinberg1}Weinberg, S., 2008, Cosmology, Oxford, 1st Edition
\bibitem[Weinberg et al(2013)]{weinberg2}Weinberg, D., H., Mortonson, M., J., Eisenstein, D., J.,Hirata, C., Riess, A., G., Rozo, E., 2013, Observational Probes of Cosmic Acceleration, arXiv:1201.2434v2
\bibitem[Zheng et al(2014)]{zheng}Zheng, W., Li, S., Xia, J., Li, M., Lu, T., 2014, Constraints on Dark Energy: New Observations including Pan-STARRS, arXiv:1405.2724v2
\end{thebibliography}
\end{document}
